\documentclass[../DoAn.tex]{subfiles}
\begin{document}

\begin{center}
    \Large{\textbf{ABSTRACT}}\\
\end{center}
\vspace{1cm}
\hspace{\parindent}Currently, while the global gaming industry is experiencing massive growth, the Vietnamese game industry has yet to make a strong breakthrough. One of the biggest barriers is the excessively high production cost. Furthermore, skyrocketing licensing fees for professional software tools (such as Windows OS, Photoshop, 3D software, etc.), coupled with the government's stricter copyright enforcement, make it even more challenging for independent (indie) developers or small studios to operate and achieve high-quality results. To tackle this budget limitation, common approaches include developing traditional 2D games, utilizing simplified low-poly art styles, or relying heavily on risky crowdfunding campaigns.

Instead of following these conventional methods, this project takes a novel approach: maximizing the ecosystem of high-quality, low-cost, or weekly free assets available on Unreal Engine 5 (UE5) to develop a 3D action game named "Paradox Caliber". The choice of UE5 is highly motivated not only by its graphical capabilities but also by its indie-friendly licensing model: Epic Games allows developers to use the engine entirely for free, exacting no royalties until the game generates a high milestone of revenue. The core motivation behind this approach is to fundamentally solve the initial funding problem, freeing indie teams to create seamlessly and attain premium visual quality without exhausting their financial resources.

The overview of this solution is not exclusively about building a functional game based on these assets but also architecting an expandable quest system. By integrating a standardized quest design with new environmental assets, developers can effortlessly configure and deploy a new level within a very short timeframe. From the initial chapters covering surveys, design, and technologies, this thesis will elucidate this process. It provides concrete experimental evidence and valuable contributions, providing robust motivation for independent developers to create games with modern graphics.

\end{document}